%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{hyperref}
\newcommand{\dollar}{\mbox{\textdollar}}
\newcommand\tab[1][1cm]{\hspace*{#1}}

 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Varun}{Rajaram}{\href{mailto:varunrajaram@gmail.com}{varunrajaram@gmail.com} | 832.857.3031 | \href{mailto:vrajaram@cs.utexas.edu}{vrajaram@cs.utexas.edu}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Experienced with:}
Java \textbullet{} Python  \\

\location{Exposure to:}
Matlab \textbullet{} R \textbullet{} 
 Tensorflow \\ \textbullet{} OpenCV \textbullet{} Arduino \textbullet{} \LaTeX\ \\
\vspace{\topsep} 

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\location{Jerry R. Junkins Memorial \\ Scholarship Award}
\vspace{1 mm}
\underline{Recipient} of scholarship awarded by \\ \textbf{\href{https://goo.gl/Yi8edi}{Texas Instruments}} to  National \\ Merit Scholarship Finalists. \\
\vspace{\topsep}
\vspace{1 mm}
\location{US State Department Scholarship}
\vspace{1 mm}
Awarded \underline{American Youth Leadership} \underline{Program} Scholarship for 5 week, all-expenses-paid study abroad and community service in Ecuador. Program selected 18 students in the Greater Houston Area. \\
\vspace{\topsep} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Miscellaneous
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Misc. Projects}
\underline{Handwritten Digit Recognition} in Python \\
\vspace{3 mm}
\begin{tightemize}
\item Use of feed-forward neural network to classify handwritten digits. 
\end{tightemize}
\vspace{1 mm}
\underline{Android Application} for high school volunteering with Android Studio
\begin{tightemize}
\item Built an application with integrated calendar and event creation mechanisms. 
\end{tightemize}
\vspace{1 mm}
\underline{Image Manipulation} in Java \\
\vspace{1 mm}
\underline{Markov chains} for Text in Java \\
\vspace{1 mm}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2 mm}
\section{Links} 
\href{github.com/v-rajaram}{Github: github.com/v-rajaram} \\
\vspace{1 mm}
\href{linkedin.com/in/varun-rajaram}{LinkedIn: linkedin.com/in/varun-rajaram}
%Github:// \href{https://github.com/v-rajaram}{\bf v-rajaram} \\
%LinkedIn://  \href{https://www.linkedin.com/in/varun-rajaram}{\bf varun-rajaram} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2 mm}
\section{Languages}
English, Spanish, Tamil \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\vspace{2 mm}
\runsubsection{University of Texas at Austin}
\descript{| BS C.S.- Turing Scholars and Dean's Scholars Honors Programs  | BA Plan II Honors Program}
\location{Aug 2017 - Present | Austin, TX}
\vspace{\topsep} 
\begin{tightemize}
\item Relevant Coursework (H = Honors version of the class):
Data Structures H, Discrete Math H, Vector Calculus H
\end{tightemize}
\vspace{4 mm}
\runsubsection{William P. Clements High School}
\descript{| Global Studies Academy} 
\location{August 2013 - June 2017 | Sugar Land, TX}
\begin{tightemize}
\item Vice President of \underline{\href{https://www.fortbendisd.com/globalstudies}{Global Studies Academy}} Magnet Program
\vspace{1 mm}
\item 5 time Model United Nations 'Best Delegate'
\vspace{1 mm}
\item Relevant Coursework: AP Computer Science A, Computer Science 3 (Data Structures and Algorithms), Computer Science 4 (Independent Study), Multivariable Calculus.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2 mm}
\section{Experience}
\vspace{2 mm}

\runsubsection{M.D. Anderson Cancer Center}
\descript{| Research Intern }
\location{June 2016 - August 2017 | Houston, TX}
\begin{tightemize}
\item Worked in Diagnostic Radiology applying \underline{deep learning} to cancer imaging, with a focus on MRI's and PET-CT Scans.
\vspace{1 mm}
\item Initial projects involved MRI flare detection and histopathology image analysis.
\vspace{1 mm}
\item Used OpenCV, Tensorflow, and Python for neural network applications.
\vspace{1 mm}
\item Pursued further research into Low-Grade Gliomas and signaling pathways, applying \underline{machine learning} to genomic sequencing, using Python and R.
\end{tightemize}
\sectionsep
\vspace{2 mm}
\runsubsection{Fort Settlement Middle School Coding Club}
\descript{| Founder of Afterschool Club}
\location{August 2015 – June 2016 | Sugar Land, TX}
\begin{tightemize}
\item Founded \underline{\href{https://goo.gl/KF7umR}{Coding Club}} for students at a local middle school, teaching fundamental computer science skills.
\vspace{1 mm}
\item Began teaching students to work with Scratch, and eventually progressed onto Java. Coding Club still exists today.
\end{tightemize}
\sectionsep
\vspace{2 mm}
\runsubsection{Global Issues Summit}
\descript{| Co-Coordinator}
\location{August 2016 – April 2017 | Sugar Land, TX}
\begin{tightemize}
\item Co-Coordinated an entirely student-run conference focusing on the United Nations Sustainable Development Goals.
\vspace{1 mm}
\item Conference had over 700 attendees from around the community.
\vspace{1 mm}
\item Extensive use of Microsoft Powerpoint, Excel, and Word (and Google Drive Equivalents).
\vspace{1 mm}
\item \url{globalissuessummit.org}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\vspace{2 mm}
[1] Garg N, Elshikh M, Rayan J, Rajaram V and Bhosale P: \underline{\href{https://www.clinicsinoncology.com/pdfs_folder/cio-v1-id1088.pdf}{Differentiating Pancreatic Cystic Lesions}} \textit{Clinics in Oncology,} in press.

\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}